\textbf{ Mapping stellar surfaces\\ I: Degeneracies in the rotational light curve problem }

### 2021-01-23 paper1/ms.tex
a little more text

@@

\xxx{This is similar to what \citet{Rauscher2018} did.}

\xxx{Remember to cite \citet{Walkowicz2013}.}

@@

\section{Conclusions}

>>>>

\xxx{This paper is also similar to \citet{Walkowicz2013} and \citet{Basri2018},
    but we approach things from a purely theoretical point of view, as opposed
    to the more empirical, qualitative approach of those two papers.}

@@

\xxx{Discuss how this is somewhat similar to what \citet{Rauscher2018} did.}

@@

\section{Discussion and conclusions}
